Training a Gaming Agent on Brainwaves

### 2020-10-13 review2/response.letter.tex

Comments to the Author
The authors have satisfactorily addressed my concerns. I have a minor comment regarding Figure 3. It is unclear what the brown bar labelled GrandAvg represents since there is one for each participant. Please clarify. I suggest having another set of bars (a ninth) for the grand average (average over participants) for each of the algorithms used.

\subsection*{\ovalbox{AE General Comments}}
AE's Comments to Author:

Associate Editor
Comments to the Author:
The paper is improved but would benefit from a further update to
- improve abstract

\begin{quotation}
{\color{blue}
We rewrote the abstract explaining in further details the obtained results.  
}
\end{quotation}

@@

- provide further interpretation/discussion of findings

\begin{quotation}
{\color{blue}
We included extra information and verified the contributions/findings.
}
\end{quotation}

@@

- fix minor errors/typos

\begin{quotation}
{\color{blue}
We fixed the carefully reported issues gently provided by Reviewers.
}
\end{quotation}

@@

- address the grand average recommendation

\begin{quotation}
{\color{blue}
We addressed this issue.  We think there must a missunderstanding from our side of the suggestion/recommendation of the Reviewer.  We added additional information in this response letter, and apologize for this.
}
\end{quotation}

@@

Comments to the Author

The paper is improved. The contribution is clearer. Thank you for the reply to comments. I attach some further comments.

The authors have satisfactorily addressed my concerns. I have a minor comment regarding Figure 3. It is unclear what the brown bar labelled GrandAvg represents since there is one for each participant. Please clarify. I suggest having another set of bars (a ninth) for the grand average (average over participants) for each of the algorithms used.

\begin{quotation}
{\color{blue}
We think we misunderstood previous Reviewer suggestions.  We added the brown bar on the previous Figure 3 (now Figure 5) because we assumed the Reviewer was referring to perform a classification using epoched averaged signal segments.  We used 5-segments to obtain an averaged signal with an enhanced signal-to-noise ratio (Wim van Drongelen, 4 - Signal Averaging, Editor(s): Wim van Drongelen, Signal Processing for Neuroscientists, Academic Press, 2007, Pages 55-70,) per Participant, and perfomed the classification of ErrP components based on those averaged signals for each Participant.  We used only Logistic Regression as classificiaton algorithm, as it was the one where we achieved better performance for single signal segments.   We think this is now confusing and decided to remove those brown bars.   
We have now included a new Figure 3, where we plotted the Grand Average signals over participants for the two experimental conditions.  The top subfigure shows the signals for the "move closer to the target" condition, whereas the bottom subfigure represents the grand average for the "move closer" condition.  
On the other hand, Figure 9 shows the results of using information to train a classifier with data from one Participant and use it to identify rewards for another participant.  This is performed in a single-trial, without any signal averaging.  
We apologize for the Reviewer for our misunderstanding and ask back for more information if it feels like the misunderstanding persisted.
}
\end{quotation}

\vskip+1ex
\noindent \dotfill
\vskip+1ex
\bibliographystyle{IEEEtran}
%\bibliography{Reference}

### 2020-10-13 review2/response.letter.tex

\subsection*{\ovalbox{Reviewer 1 General Comments}}

Comments to the Author
The paper is improved. The contribution is clearer. Thank you for the reply to comments. I attach some further comments.

Training a Gaming Agent on Brainwaves
The paper has been improved. IMO, there are still areas that need further attention to improve the paper further.
Page 1
The abstract still reads like an introduction until the last sentence.  I would begin with sentence: “Error-related potential (ErrP) are a particular type of ERP that can be elicited by a person who attends a recognizable error.”

\begin{quotation}
{\color{blue}
We started the abstract as suggested, and rewrote it detailing the obtained results.   Thank you very much for your suggestion.
}
\end{quotation}

@@

Expand the results of the paper as this is the contribution.
“Results show that there is an  \underline{effective} transfer of information and that the agent learns \underline{successfully} to solve the game efficiently.
Both the underlined terms need to cite evidence from the paper.

\begin{quotation}
{\color{blue}
We included the following information in the abstract and added it in the Conclusions Section (IV), showing evidence from the paper.

Each time the gaming agent plays this simple game, it takes on average around 100 steps to reach the target spot.  We trained a classifier to recognize Error Potential from observational human critics that watch the agent playing the game.  We let the agent play again and we mark movements that trigger an error potential from the human critic.  We used those movements as rewards in a Reinforcement Learning scheme, and use them to train a Q-Table.  When we let the agent plays the game again, the number of steps that requires to solve the game is now reduced.  If we provide feedback based on random signals, we verified that no reduction is achieved and the average number of steps does not change.   This shows that there is an effective transfer of information from the brainwaves to the agent.   As this process is repeated, the agent keeps improving solving the game effectively, i.e. performing the minimum number of required steps to reach the goal.

}
\end{quotation}

@@

Line 40 “This information is used to make a gaming agent $<$that$>$ improves ....”

\begin{quotation}
{\color{blue}
This text is no longer contained in the manuscript.  We verified throughout the Manuscript to avoid similar mistakes.
}
\end{quotation}

@@

Line 58 Put in a reference number from ethics committee from which approval was sough (e.g. University committee)

\begin{quotation}
{\color{blue}
We added the missing information on Section II.A.  Thanks for pointing out this important issue.
}
\end{quotation}

Page 2
Line 56 “Data \sout{is} $<$are$>$ handled and processed with the OpenVibe Designer,” // datum-data

\begin{quotation}
{\color{blue}
Fixed issue for every appearances of \textbf{data}.
}
\end{quotation}

@@

Page 4
Lin 24 This allows \sout{to learn} the Q-Table $<$to learn$>$ based on the subject’s feedback from the movements the agent
took, which are chosen pseudo-randomly, while executing the brainwave session.

\begin{quotation}
{\color{blue}
Fixed issue.  We appreciate a lot the level of detail in the comments.
}
\end{quotation}

Line 50 “The best overall performance is obtained using Logistic Regression.” // also need to discuss the significance of the overall levels of accuracy in Discussion. Is a best performance of 0.672 useful/acceptable? How does it compare to other researchers (if a comparison is possible).

\begin{quotation}
{\color{blue}
On Section IV, third paragraph we tackled this issue.  The overall performance of 0.672 is low.  Although a comparison can be misleading in the context of the ErrP experiment, we added a brief comparison to other similar works.  We also emphasized this point in future  works at the end of the Conclusions section.
}
\end{quotation}

@@

Line 42 col 2 “These results are also consistent with their classification ROC curves, shown \sout{on} $<$in$>$ Figures 6 obtained for both subjects, where the area under the curve are close to chance level.” // Why didn’t you show one good ROC curve and one bad one. This would provide the basis for comparison.

\begin{quotation}
{\color{blue}
Due to previous Reviewer's requests, we added all the ROC curves on the new Figure 7.  We now emphasized on this figure's caption which ROC curves where showing an effective identification of the ErrP potential and which did not.  We added this in the text emphasizing the important finding that we could not provide an enhancement of the agent performance based on the rewards from subjects where the obtained ROC curves were not good.
}
\end{quotation}

@@

Comments to the Author

The paper is improved. The contribution is clearer. Thank you for the reply to comments. I attach some further comments.

The authors have satisfactorily addressed my concerns. I have a minor comment regarding Figure 3. It is unclear what the brown bar labelled GrandAvg represents since there is one for each participant. Please clarify. I suggest having another set of bars (a ninth) for the grand average (average over participants) for each of the algorithms used.

\begin{quotation}
{\color{blue}
We think we misunderstood previous Reviewer's suggestions.  We added the brown bar on the previous Figure 3 (now Figure 5) because we assumed the Reviewer was referring to perform a classification using epoched averaged signal segments.  We used 5-segments to obtain an averaged signal with an enhanced signal-to-noise ratio (Wim van Drongelen, 4 - Signal Averaging, Editor(s): Signal Processing for Neuroscientists, Academic Press, 2007, Pages 55-70,) per Participant, and performed the classification of ErrP components based on those averaged signals for each Participant.  We used only Logistic Regression as classification algorithm, as it was the one with which we achieved better performance for single signal segments.   It is clear now that the brown bars were confusing and we have decided to remove them.  
Instead, we have now included a new Figure 3, where we plotted the \textbf{Grand Average} signals over all the participants for the two experimental conditions.  The top subfigure shows the signals for the "move closer to the target" condition, whereas the bottom subfigure represents the grand average for the "move further" condition.  
On the other hand, Figure 9 shows the results of using information to train a classifier with data from one Participant and use it to identify rewards for another participant.  This is performed in a single-trial approach from individual segments without any signal averaging.  
We apologize to the Reviewer for our misunderstanding and ask back for more information if it feels like the misunderstanding persisted.
}
\end{quotation}

\vskip+1ex
\noindent \dotfill
\vskip+1ex
\bibliographystyle{IEEEtran}
%\bibliography{Reference}

### 2020-10-13 ErrP.tex
Más respuestas.  Finalmente decidí volar el gráfico de los promedios.  En un punto no es lo que el revisor exactamente pide y lo que el pide no me parece, y creo comparten ustedes, tenga mucho sentido hacerlo.  Prefiero ir por el lado de ofrecerle alternativas y presentar el gráfico del grand average que es lo que quizás aporte más info (además ese gráfico salió perfecto).
Una vuelta de rosca.

Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during task execution. The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled with brain signals from a person who is observing a robot solve a task.  Moreover, a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour~\cite{Luo2019}, to assess air traffic controller's decisions~\cite{Goh2019} or to categorize actions as errors~\cite{Wirth2020}. Other approaches have used these signals as important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018}.  Additionally, ErrPs have also been used in the context of games as an additional feedback channel that can be explored to improve gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.   The game is similar to this one \cite{Iturrate2013}.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.5\textwidth]{revisedimages/avg_closer.eps}
    \includegraphics[width=0.5\textwidth]{revisedimages/avg_further.eps}
    \caption{Grand Average for all OHCs for the closer and further condition.  It can be seen the bump around 300 ms.}
    \label{fig:classifiers}
\end{figure}

Figure~\ref{fig:classifiers} shows the binary classification accuracy obtained for the eight OHCs using five different classification algorithms and using a 10-fold cross-validation procedure.  The best overall performance is obtained using Logistic Regression.  In addition, the classification accuracy obtained averaging 5 epochs is shown as well.  Although the signal averaging procedure improves the Signal-To-Noise-Radio (SNR) of the ErrP response, it reduces the number of data samples, producing a clear improvement only for the OHCs that contain more samples (1, 3 and 7).

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.11]{revisedimages/cross_val.eps}
    \includegraphics[scale=0.21]{revisedimages/avg_5_segments.eps}
    \caption{Binary single trial classification score using five different classifiers while recognizing ErrP potentials for the eight OHCs.  The classification score using an ensemble average of 5 epochs is shown as well (GrandAvg). Chance Level is 0.5.}
    \label{fig:classifiers}
\end{figure}

@@

\begin{figure}[h!]
\captionsetup[subfigure]{justification=centering}
\begin{subfigure}{0.5\textwidth}
\centering
\includegraphics[scale=0.09]{revisedimages/roc_1.eps}   \hspace{-1.5em}
\includegraphics[scale=0.09]{revisedimages/roc_2.eps} \\
%\vspace{-1.3em}
\centering
\includegraphics[scale=0.09]{revisedimages/roc_3.eps}   \hspace{-1.5em}
 \includegraphics[scale=0.09]{revisedimages/roc_4.eps} \\
 \centering
  \includegraphics[scale=0.09]{revisedimages/roc_5.eps}   \hspace{-1.5em}
  \includegraphics[scale=0.09]{revisedimages/roc_6.eps} \\
  \centering
  \includegraphics[scale=0.09]{revisedimages/roc_7.eps}    \hspace{-1.5em}
  \includegraphics[scale=0.09]{revisedimages/roc_8.eps} \\
\end{subfigure}
\caption{ROC Curves for OHCs 1-8. True positive rate is on the vertical axis and false positive rate on the horizontal axis.}
\label{fig:rocsubjects}
\end{figure}

@@

>>>>

Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during task execution. The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled with brain signals from a person who is observing a robot solve a task.  Moreover, a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour~\cite{Luo2019}, to assess air traffic controller's decisions~\cite{Goh2019} or to categorize actions as errors~\cite{Wirth2020}. Other approaches have used these signals as important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018,Iturrate2013}.  Additionally, ErrPs have also been used in the context of games as an additional feedback channel that can be explored to improve gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.5\textwidth]{revisedimages/avg_closer.eps}
    \includegraphics[width=0.5\textwidth]{revisedimages/avg_further.eps}
        \includegraphics[scale=1.0]{revisedimages/electrodes.png}
    \caption{Grand Average of 2-seconds segments for all OHCs for the "move closer" (top) and "move further" (middle) condition.  The increased height of the first peak around 0.4 seconds reflects the Error Potential response particularly on Pz, based on the electrode layout (bottom).}
    \label{fig:classifiers}
\end{figure}

Figure~\ref{fig:classifiers} shows the binary classification accuracy obtained for the eight OHCs using five different classification algorithms and using a 10-fold cross-validation procedure.  The best overall performance is obtained using Logistic Regression.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.5\textwidth,height=70pt]{revisedimages/cross_val.eps}
    %\includegraphics[width=290pt,height=90pt]{revisedimages/avg_5_segments.eps}
    \caption{Binary single trial classification score using five different classifiers while recognizing ErrP potentials for the eight OHCs.   Chance Level is 0.5.}
    \label{fig:classifiers}
\end{figure}

@@

\begin{figure}[h!]
\captionsetup[subfigure]{justification=centering}
\begin{subfigure}{0.5\textwidth}
\centering
\includegraphics[scale=0.09]{revisedimages/roc_1.eps}   \hspace{-1.5em}
\includegraphics[scale=0.09]{revisedimages/roc_2.eps} \\
%\vspace{-1.3em}
\centering
\includegraphics[scale=0.09]{revisedimages/roc_3.eps}   \hspace{-1.5em}
 \includegraphics[scale=0.09]{revisedimages/roc_4.eps} \\
 \centering
  \includegraphics[scale=0.09]{revisedimages/roc_5.eps}   \hspace{-1.5em}
  \includegraphics[scale=0.09]{revisedimages/roc_6.eps} \\
  \centering
  \includegraphics[scale=0.09]{revisedimages/roc_7.eps}    \hspace{-1.5em}
  \includegraphics[scale=0.09]{revisedimages/roc_8.eps} \\
\end{subfigure}
\caption{ROC Curves for OHCs 1-8. True positive rate is on the vertical axis and false positive rate on the horizontal axis.  The ROC curves for ErrP identification for Subjects 5 and 6 show low classification scores.}
\label{fig:rocsubjects}
\end{figure}

@@

Each time the gaming agent plays this simple game, it takes on average around 100 steps to reach the target spot.  We trained a classifier to recognize Error Potential from observational human critics that watch the agent playing the game.  We let the agent play again and we mark movements that trigger an error potential from the human critic.  We used those movements as rewards in a Reinforcement Learning scheme, and use them to train a Q-Table.  When we let the agent plays the game again, the number of steps that requires to solve the game is now reduced.  If we provide feedback based on random signals, we verified that no reduction is achieved and the average number of steps does not change.   This shows that there is an effective transfer of information from the brainwaves to the agent.   As this process is repeated, the agent keeps improving solving the game effectively, i.e. performing the minimum number of required steps to reach the goal.
